### 2024-01-04 README.Rmd
updated createHOT - 240201
updated vignette and markdown - 240104

The goal of `validateHOT` is to provide a tool to validate the results
of your validation task (also known as holdout task; short form
**HOT**), simulating markets with the results of your MaxDiff, CBC, and
ACBC, and lastly to convert the raw logit scores of your MaxDiff, CBC,
and ACBC into scores that are easier to communicate. This package is
especially relevant for the [Sawtooth
Software](https://sawtoothsoftware.com/) community who would like to
report their analysis in *R* for open science purposes. However, it also
works perfectly with the great package `ChoiceModelR`(Sermas, 2022).
This package is extremely useful for practitioners, who would like to
run the analyses in an open source software. The ultimate goal of these
preference measurement techniques is to predict future behavior (Green &
Srinivasan, 1990). Therefore, it is essential for both academics and
practitioners to ensure that the collected data is valid and can also
predict outside tasks that were not included in the estimation of the
utility scores.

@@

👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data
and running your initial Hierarchical Bayes models, you can turn to
`validateHOT` and test how good your model predicts choices in the
validation/holdout task. Therefore, you only have to read in your raw
utility scores as well as the actual choice of your validation/holdout
task. You can use the `merge()` function provided by the *R* base
package to do so (R Core Team, 2023). Afterward, you can read in your
data file and enjoy `validateHOT`. We provide a short tutorial in the
markdown, for a more detailed tutorial, please see the vignette that
comes along with `validateHOT`.

👈🏾 <u>**What you get**</u>:<br> At the moment, `validateHOT` provides
functions for 4 key areas:

@@

For all 4 key areas, the `createHOT()` function is essential. This
function creates the total utilities for each alternative in the
validation/holdout task and also in the simulation method, respectively.
Rao (2014, p. 82) mentions the additive utility model stating that the
total utility of a profile or conjoint model is the sum of its attribute
levels. `createHOT()` will calculate the total utility of each
alternative you specify.

@@

We also include metrics from machine learning, i.e., the confusion
matrix (e.g., Burger, 2018). For all of the five provided functions, a
**none** alternative has to be included in the validation/holdout task.
The logic of the implemented confusion matrix is to test, for example,
whether a buy or no-buy was correctly predicted. Information could be
used to get a sense of overestimation and underestimation, respectively,
of product demand. In the table below <code>TP</code> stands for true
positives, <code>FP</code> for false positives, <code>TN</code> for true
negatives, and <code>FN</code> for false negatives (Burger, 2018; Kuhn,
2008). To translate this to the `validateHOT` logic, imagine you have a
validation/holdout task with five alternatives plus the alternative not
to buy any of those chosen. `validateHOT` now measures whether or not a
buy (participant opts for one of the five alternatives) or a no-buy
(participant opts for the none alternative), respectively, is correctly
predicted.

@@

Again, all functions can be extended with the `group` argument to get
output split by group(s).

@@

<li><code>zero_anchored()</code></li>

: Rescales the raw logits of a MaxDiff to zero-centered diffs (Chrzan &
Orme, 2019, p. 64).

@@

We are teaching a preference measurement seminar for students. Often
these students did not have any prior experience (or only sparsely) with
*R*. One of the chapters in this class is about model validation by
checking holdout task and we teach this, of course, in *R* 😍. We want
to put a strong emphasis on open science and providing tools to run the
analyses and provide the code afterwards is essential. `validateHOT`
makes this process look easy.

Of course, there are other great packages which are faster in terms of
running time (i.e., `Metrics` by Hamner & Frasco, 2018), however, these
packages need some more data wrangling in order to use the appropriate
functions with the raw utilities, which might be a burden or barrier for
the one or the other.

@@

Now imagine you included a validation/holdout task with three
alternatives plus a no-buy alternative. We specify the `data` argument
and as well as the `id`. Since we also have a *no-buy* alternative in
our validation task, we next specify the `none` argument, otherwise we
would have left it empty. Afterwards, we define each alternative with
the argument `prod.levels`. If we look back at the data frame, we can
see that the first alternative in the holdout task (`c(4, 9, 19)`) is
composed of the following attribute levels `Att1_Lev1`, `Att2_Lev1`, and
`Att3_Lev5`.

@@

> ❗ `createHOT()` takes both column names and column indexes. However,
> please be aware, if you include linear-coded or piecewise-coded, you
> **have** to provide the column indexes for the input in `prod.levels`.
> However, you can easily find out the index by either using the
> `names()` function to see all names of the data frame, or if you
> already know the name of the variable, you can use `which()` and
> `colnames()`, both functions are provided by the base package (R Core
> Team, 2023). For example, if you want to find out the column index of
> `ID`, you could run `which(colnames(CBC) == "ID")` to determine the
> column index of `ID`.

@@

@@

To cover also one example on how to use the metrics of the confusion
matrix, we could test whether our model overestimates the purchase
behavior (our model predicts a *buy* although participant opts for a
*no-buy*) or underestimates it (i.e., model predicts *no-buy* but
participant opts for a *buy*). We will test the accuracy of the model by
running the `accuracy()` function.

@@

Again, we first define data, namely the `id` as well as the `none`
alternative. Next, we define the `prod.levels` for each alternative.
Since we have one linear coded attribute, we have to specify the column
indexes instead of the column names. For example, for the second
alternative which is composed of `Att1_Lev5`, `Att2_Lev4`, and `60`
which is the value that should be interpolated. We tell `createHOT()`
that this value needs to be interpolated by specifying the `coding`
argument accordingly. This tells us that the first two attributes
(`Att1_Lev5`, `Att2_Lev4` in the case of alternative 2) are part-worth
coded (`0`) while the third attribute is linear-coded (`1`).

@@

Next, we define the column index of the linear coded variable (`lin.p`)
and specify the `coding` we talked about above. Again, we are running a
*CBC* specified by the `method` argument. This time, we would like to
keep some of the variables in the data frame, which we specify in
`varskeep`. We only keep one further variable, however, you can specify
as many as you want. This could be relevant if you would like to display
results per group. Finally, we define the actual choice (`choice`) in
the holdout/validation task and we are all set.

@@

>>>>

The goal of `validateHOT` is to provide a tool to validate the results
of your validation task (also known as holdout task; short form
**HOT**), simulating markets with the results of your MaxDiff, CBC, and
ACBC, and lastly converting the raw logit scores of your MaxDiff, CBC,
and ACBC into scores that are easier to communicate. This package is
especially relevant for the [Sawtooth
Software](https://sawtoothsoftware.com/) community who would like to
report their analysis in *R* for open science purposes. However, it also
works perfectly with the package `ChoiceModelR`(Sermas, 2022). This
package is extremely useful for practitioners, who would like to run the
analyses in an open source software. The ultimate goal of these
preference measurement techniques is to predict future behavior (Green &
Srinivasan, 1990). Therefore, it is essential for both academics and
practitioners to ensure that the collected data is valid and can also
predict outside tasks that were not included in the estimation of the
utility scores.

@@

👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data
and running your initial Hierarchical Bayes models, you can turn to
`validateHOT` and test how good your model predicts choices in the
validation/holdout task, run market simulations, or convert your data
into scores which are easier to interpret. To enjoy `validateHOT` you
only have to read in your raw utility scores. If you plan to validate
your validation/holdout tasks you also need to provide the actual choice
of your validation/holdout task. You can use the `merge()` function
provided by the *R* base package to do so (R Core Team, 2023). We
provide a short tutorial in the markdown, for a more detailed tutorial,
please see the vignette that comes along with `validateHOT`.

👈🏾 <u>**What you get**</u>:<br> At the moment, `validateHOT` provides
functions for 4 key components:

@@

For the first 3 components, the `createHOT()` function is essential.
This function creates the total utilities for each alternative in the
validation/holdout task and also in the simulation method, respectively.
Rao (2014, p. 82) mentions the additive utility model stating that the
total utility of a profile or conjoint model is the sum of its attribute
levels. `createHOT()` will calculate the total utility of each
alternative you specify.

@@

We also include metrics from machine learning, i.e., the confusion
matrix (e.g., Burger, 2018). For all of the five provided functions, a
**none** alternative has to be included in the validation/holdout task.
The logic of the implemented confusion matrix is to test, for example,
whether a buy or no-buy was correctly predicted. Information could be
used to get a sense of overestimation and underestimation, respectively,
of general product demand. In the table below <code>TP</code> stands for
true positives, <code>FP</code> for false positives, <code>TN</code> for
true negatives, and <code>FN</code> for false negatives (Burger, 2018;
Kuhn, 2008). To translate this to the `validateHOT` logic, imagine you
have a validation/holdout task with five alternatives plus the
alternative not to buy any of those alternatives. `validateHOT` now
measures whether or not a buy (participant opts for one of the five
alternatives) or a no-buy (participant opts for the none alternative),
respectively, is correctly predicted.

@@

Again, all functions can be extended with the `group` argument to get
the output split by group(s).

@@

<li><code>zero_anchored()</code>: Rescales the raw logits of a MaxDiff
to zero-centered diffs (Chrzan & Orme, 2019, p. 64).</li>

@@

We are teaching a preference measurement seminar for students. Often
these students did not have any prior experience (or only sparsely) with
*R*. One of the chapters in this class is about model validation by
checking holdout task and we teach this, of course, in *R* 😍. We want
to put a strong emphasis on open science and providing tools to run the
analyses and provide the code afterwards is essential. `validateHOT`
makes this process look easy 🤹‍♀️. Of course, there are other great
packages which are faster in terms of running time (i.e., `Metrics` by
Hamner & Frasco, 2018), however, these packages need some more data
wrangling in order to use the appropriate functions with the raw
utilities, which might be a burden or barrier for the one or the other.

@@

Now imagine you included a validation/holdout task with three
alternatives plus a no-buy alternative. We specify the `data` argument
and as well as the `id`. Since we also have a *no-buy* alternative in
our validation task, we specify the `none` argument, otherwise we would
have left it empty. Afterwards, we define each alternative with the
argument `prod.levels`. If we look back at the data frame, we can see
that the first alternative in the holdout task (`c(4, 9, 19)`) is
composed of the following attribute levels `Att1_Lev1`, `Att2_Lev1`, and
`Att3_Lev5`.

@@

> ❗ `createHOT()` takes both column names and column indexes. However,
> please be aware, if you include linear-coded or piecewise-coded, you
> **have** to provide the column indexes for the input in `prod.levels`.
> However, you can easily find out the index by either using the
> `names()` function to see all names of the data frame, or if you
> already know the name of the variable, you can use `which()` and
> `colnames()`, both functions are provided by the base package (R Core
> Team, 2023). For example, if you want to find out the column index of
> `ID`, you could run `which(colnames(CBC) == "ID")`.

@@

> In case you just need to create a market scenario, you can also leave
> the `choice` argument empty.

@@

To cover also one example on how to use the metrics of the confusion
matrix, we could test whether our model overestimates the purchase
behavior (our model predicts *buy* although participant opts for
*no-buy*) or underestimates it (i.e., model predicts *no-buy* but
participant opts for *buy*). We will test the accuracy of the model by
running the `accuracy()` function.

@@

Again, we first define data, namely the `id` as well as the `none`
alternative. Next, we define the `prod.levels` for each alternative.
Since we have one linear coded attribute, we have to specify the column
indexes instead of the column names in `prod.levels`. For example, for
the second alternative which is composed of `Att1_Lev5`, `Att2_Lev4`,
and `60` which is the value that should be interpolated. We tell
`createHOT()` that this value needs to be interpolated by specifying the
`coding` argument accordingly. This tells us that the first two
attributes (`Att1_Lev5`, `Att2_Lev4` in the case of alternative 2) are
part-worth coded (`0`) while the third attribute is linear-coded (`1`).

@@

Next, we define the column index of the linear coded variable (`lin.p`).
Again, we are running a *CBC* specified by the `method` argument. This
time, we would like to keep some of the variables in the data frame,
which we specify by using the `varskeep` argument. We only keep one
further variable, however, you can specify as many as you want. This
could be relevant if you would like to display results per group.
Finally, we define the actual choice (`choice`) in the
holdout/validation task and we are all set.

@@

Lastly, this time we also want to use a rescaling function, namely
`att_imp()` which basically tells us the importance of each attribute
included (Orme, 2020). We need the data set with the raw logit
coefficients (`CBC_lin`). Next, we define the `attrib` argument. Here,
we need to specify each attribute level for the corresponding level.
Afterwards, we specify the coding again, and since we have one linear
coded attribute, we need to define the `interpolate.levels` argument
again, as we did for the `createHOT()` function above. Finally, we set
`res` to `agg`, which tells `att_imp()` to display the aggregated
results (for individuals results set `agg` to `ind`).

```{r}
att_imp(
  data = CBC_lin,
  attrib = list(
    c("Att1_Lev1", "Att1_Lev2", "Att1_Lev3", "Att1_Lev4", "Att1_Lev5"),
    c("Att2_Lev1", "Att2_Lev2", "Att2_Lev3", "Att2_Lev4", "Att2_Lev5"),
    c("Att3_Lin")
  ),
  coding = c(0, 0, 1),
  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
  res = "agg"
)
```
